Pricing Approaches for Green Tea Products

### 2024-11-21 paper/paper.qmd
Aligned citation style, now all citations are before the period

The graphing scripts in this paper are written in R [@citeR], with the tidyverse package [@tidyverse] The graphs are generated with ggplot2 [@ggplot2].Data cleaning was done in SQL [@citeSQL].

@@

## Mesurement
The data used in this paper were obtained from the websites of various food retail companies, including Voila, T&T, Loblaws, No Frills, Metro, Galleria, Walmart Canada, Save-On-Foods. The data was gathered by using screen-scrape of website UI, starting from Feb.28 to Nov.14. This data captures the product name, units, and prices of each vendors. [@raw_data_source] This data set is designed to be sited for suitable for academic analysis on market behaviors and for legal actions.

@@

A more comprehensive study that includes these smaller retailers is required to understand small firms that does rececive less benefit from economy of scale and may be focused to serve local residents.

as it is likely that the dataset is skewed toward the most commonly sold items at major chains, which are typically mass-produced and mainstream products. And are easier to collect data and remember to include. Smaller stores often feature more niche items, locally sourced goods, or specialty products that cater to specific communities or tastes, which may not be represented in this dataset. These unique products could differ in terms of pricing, availability, and consumer demand, and excluding them would result in an incomplete understanding of the diversity in consumer preferences and retail offerings. A more comprehensive study can also foucs on including more types of good for a full analysis.

>>>>

The graphing scripts in this paper are written in R [@citeR], with the tidyverse package [@tidyverse] The graphs are generated with ggplot2 [@ggplot2]. Data cleaning was done in SQL [@citeSQL].

@@

## Mesurement
The data used in this paper were obtained from the websites of various food retail companies, including Voila, T&T, Loblaws, No Frills, Metro, Galleria, Walmart Canada, Save-On-Foods. The data was gathered by using screen-scrape of website UI, starting from Feb.28 to Nov.14. This data captures the product name, units, and prices of each vendors [@raw_data_source].  This data set is designed to be sited for suitable for academic analysis on market behaviors and for legal actions.

@@

A more comprehensive study that includes these smaller retailers is required to understand small firms that does receive less benefit from economy of scale and may be focused to serve local residents.

as it is likely that the dataset is skewed toward the most commonly sold items at major chains, which are typically mass-produced and mainstream products. And are easier to collect data and remember to include. Smaller stores often feature more niche items, locally sourced goods, or specialty products that cater to specific communities or tastes, which may not be represented in this dataset. These unique products could differ in terms of pricing, availability, and consumer demand, and excluding them would result in an incomplete understanding of the diversity in consumer preferences and retail offerings. A more comprehensive study can also focus on including more types of good for a full analysis.
